Quantifying Interpretability of Arbitrary Machine Learning Models Through Functional Decomposition

### 2019-07-02 2019-reisensburg/2019-reisensburg-molnar.Rmd
finalize
fixes title

---
title: "Measuring and optimizing machine learning interpretability"
author: "Christoph Molnar, Giuseppe Casalicchio, Bernd Bischl"
date: "Statistical Computing 2019-07-03"
institute: "LMU Munich"
output: 
  beamer_presentation:
    includes:
      in_header: "header_pagenrs.tex"
---

@@

## Additivity Improves Interpretation

@@

>>>>

---
title: "Quantifying Interpretability of Arbitrary Machine Learning Models Through Functional Decomposition"
author: "Christoph Molnar, Giuseppe Casalicchio, Bernd Bischl"
date: "Statistical Computing 2019-07-03"
institute: "LMU Munich"
output: 
  beamer_presentation:
    includes:
      in_header: "header_pagenrs.tex"
---

@@

@@

```
 ## Additivity Improves Interpretation
